### 2018-01-03 pubs/thesis/sections/acknowledgements.tex
[ paper ] Renamed directory.

Last but not least, I thankfully acknowledge
Andreas Abel and Chalmers University of Goteborg, Sweden for
inviting me to be part of the \Agda Implementors’ Meeting XXV
where I presented part of this research in the meeting.

>>>>

Last but not least, I thankfully acknowledge
Andreas Abel and Chalmers University of Technology at Goteborg, Sweden for
inviting me to be part of the \Agda Implementors’ Meeting XXV
where I presented part of this research in the meeting.

### 2018-01-03 pubs/thesis/sections/introduction.tex
[ paper ] Renamed directory.

An automatic theorem prover (henceforth \ATP) is a program that
intends to prove conjectures from axioms and inference rules of some
logical system. In the last decades, \ATPs are fast becoming a key
instrument in different disciplines and real applications (\eg,
verifying a railway interlocking system, an operating-system kernel,
or a pseudo-random number generator for cryptography). Since some
programming errors have been found in these programs (see, for
example, \cite{Keller2013,Bohme2011,Fleury2014}), researchers and
users from academy and industry have shown an increased interest to
\emph{formally} prove the validity of \ATPs' results.

>>>>

An automatic theorem prover (henceforth \ATP) is a program that
intends to prove conjectures from axioms and inference rules of some
logical system. In the last decades, \ATPs are fast becoming a key
instrument in different disciplines and real applications (\eg,
verifying a railway interlocking system, an operating-system kernel,
or a pseudo-random number generator). Since some
programming errors have been found in these programs (see, for
example, \cite{Keller2013,Bohme2011,Fleury2014}), researchers and
users from academy and industry have shown an increased interest to
\emph{formally} prove the validity of \ATPs' results.

### 2018-01-03 pubs/thesis/sections/notes/discussion.tex
[ paper ] Renamed directory.

\begin{verbatim}
  fof(goal, conjecture, p & r & q).
  fof(subgoal_0, plain, p, inference(strip, [], [goal])).
  fof(subgoal_1, plain, p => r, inference(strip, [], [goal])).
  fof(subgoal_2, plain, (p & r) => q, inference(strip, [], [goal])).
\end{verbatim}

>>>>

\begin{verbatim}
  fof(goal, conjecture, p & r & q).
  fof(subgoal_0, plain, p, inference(strip, [], goal)).
  fof(subgoal_1, plain, p => r, inference(strip, [], goal)).
  fof(subgoal_2, plain, (p & r) => q, inference(strip, [], goal)).
\end{verbatim}

### 2018-01-03 pubs/thesis/sections/notes/implementation.tex
[ paper ] Renamed directory.

\Agda is an interactive system for constructing proofs and programs,
based on Martin-L\"{o}f's type theory and extended with records,
parametrised modules, among other features. One of the main
strengths of \Agda is its support for writing proofs, which we shall
call \Agda's proof engine. It consists of: support for inductively
defined types, including inductive families, and function
definitions using pattern matching on such types, normalisation
during type- checking, commands for refining proof terms, coverage
checker and termination checker.

>>>>

\Agda is an interactive system for constructing proofs and programs,
based on Martin-L\"{o}f's type theory and extended with records,
parametrised modules, among other features. One of the main
strengths of \Agda is its support for writing proofs, which we shall
call \Agda's proof engine. It consists of: support for inductively
defined types, including inductive families, and function
definitions using pattern matching on such types, normalisation
during type- checking, commands for refining proof-terms, coverage
checker and termination checker.

### 2018-01-03 pubs/thesis/sections/proof-reconstruction/conjunct.tex
[ paper ] Renamed directory.

\subsubsection{Splitting a conjunct.}
\label{sssec:splitting-a-conjunct}

@@

\begin{verbatim}
  fof(p1, p ∧ q ∧ (r ∨ ¬ p), inf(canonicalize, [x])).
  fof(p2, q, inf(conjunct, [p1])).
  fof(p3, (r ∨ ¬ p), inf(conjunct, [p1])).
\end{verbatim}

In the first formula, $p ∧ q ∧ (r ∨ ¬ p)$, we find a left-associative
conjunction named \verb!p1!.
The \conjunct rule extracts $q$ from the \verb!p1! using a left
projection (∧-proj₁) follow by a right projection (∧-proj₂).
After, the \conjunct rule extracts $r ∨ ¬ p$ by using a right projection
on \verb!p1!.
\end{myexamplenum}

>>>>

\subsubsection{Conjunct.}
\label{sssec:splitting-a-conjunct}

@@

\begin{verbatim}
  fof(p₁, p ∧ q ∧ (r ∨ ¬ p), ...
  fof(p₂, q, inf(conjunct, p₁)).
  fof(p₃, r ∨ ¬ p, inf(conjunct, p₁)).
\end{verbatim}

In the first formula, $p ∧ q ∧ (r ∨ ¬ p)$, we find a left-associative
conjunction named \verb!p₁!. The \conjunct rule extracts $q$ from the
\verb!p₁! using a left projection (∧-proj₁) follow by a right
projection (∧-proj₂). After, the \conjunct rule extracts $r ∨ ¬ p$ by
using a right projection on \verb!p₁!.

\end{myexamplenum}

### 2018-01-03 pubs/thesis/sections/type-theory.tex
[ paper ] Renamed directory.

Therefore, the proof verification task becomes in type theory as
verifying that the proof-term has the correspondent type of the
theorem. We know this process as \emph{type-checking}.
This feature of type theory allow us to verify a proof generated by an \ATP by reconstructing its proof-term to type-check the proof. For such a
purpose, we use a proof-assistant based on type theory like \Agda to
delegate this task. % However, this approach has some weak points
discussed in~\cite{Bezem2002}. Some limitations from the type theory
point of view for proof-reconstruction is described in the following
sections.

@@

\begin{notation}
In the latter definitions and theorems, we  use a common notation in
type theory, pattern-matching~\cite{Coquand1992} to define by cases
on the inductive definition of types.

We adopt pattern-matching to define some functions.
These pattern-matching definitions follow the inductive definitions
of the type.
\end{notation}

@@

In~\eqref{eq:uh-definition} is a definition no structurally recursive.

@@

Therefore, one way to translate $\fuh_{0}$ to type
theory is to define a new function using a bounded recursion.

@@

\caption{Inference rules for propositional logic.}
\label{fig:CPL-inference-rules}
\end{figure}

>>>>

Therefore, the proof verification task becomes in type theory as
verifying that the proof-term has the correspondent type of the
theorem. We know this process as \emph{type-checking}.
This feature of type theory allow us to verify a proof generated by an \ATP by reconstructing its proof-term to type-check the proof. For such a
purpose, we use a proof-assistant based on type theory like \Agda to
delegate this task. % However, this approach has some weak points
discussed in~\cite{Bezem2002}. Some limitations from the type theory
point of view for proof-reconstruction is described in
Section~\ref{ssec:structural-recursion} and
Section~\ref{ssec:intuitionistic-logic}.

@@

\begin{notation}
In the latter definitions and theorems, we  use a common notation in
type theory, pattern-matching~\cite{Coquand1992} to define functions by cases on the inductive definition for the type of the arguments.
\end{notation}

@@

In~\eqref{eq:uh-definition}, the first two equations in the $\fuh_{0}$ function definition are no structurally recursive.
Note that the formula used in the recursive calls are not subformulas
of the formula in the function argument.

@@

Therefore, one way to define $\fuh_{0}$ in type
theory is to define a new function using a bounded recursion.

@@

\caption{Inference rules for classical propositional logic.}
\label{fig:CPL-inference-rules}
\end{figure}
